A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-11 paper/ms.tex
update ms

%\documentclass[12pt,twocolumn,tighten]{aastex63}
\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{
  {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored points are
  kinematically selected members of the $\delta$\,Lyr cluster (black points in
  Figure~\ref{fig:XYZvtang}).  Both Kepler (gray panels) and TESS (colored
  points) observed members of the cluster.  Gray points are naked-eye stars
  ($m_{\rm V}<6.5$), three of which are annotated.  Kepler\,1627 (green star) was
  observed for two TESS sectors, and during the entirety of the Kepler mission.
  \label{fig:skychart}
  }
\end{figure*}

@@

\input{table1.tex}

The \texttt{v0.5} CDIPS target catalog includes some important updates
from previous versions.  As in \citet{bouma_cdipsI_2019}, we collected
membership information for young, age-dated, or age-dateable stars
from across the literature.  Table~\ref{tab:metadata} gives a list of
the sources included, and some brief summary statistics.

@@

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{
  {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored points are
  kinematically selected members of the $\delta$\,Lyr cluster (black points in
  Figure~\ref{fig:XYZvtang}).  Both Kepler (gray panels) and TESS (colored
  points) observed portions of the cluster.  Gray points are naked-eye stars
  ($m_{\rm V}<6.5$), three of which are annotated.  Kepler\,1627 (green star) was
  observed during the entirety of the Kepler mission, and has (so far) been observed
  for two lunar months by TESS.
  \label{fig:skychart}
  }
\end{figure*}

@@

\input{t1_appendix.tex}
\input{t2_appendix.tex}

The \texttt{v0.5} CDIPS target catalog (Table~\ref{tab:v05}) includes
some important updates from previous versions.  As in
\citet{bouma_cdipsI_2019}, we collected membership information for
young, age-dated, or age-dateable stars from across the literature.
Table~\ref{tab:metadata} gives a list of the sources included, and
some brief summary statistics.

@@

\section{Kinematic Selection of $\delta$\,Lyr Cluster Members}

Figure~\ref{fig:XYZvtang} shows members of the \cn\
reported
by \citet{kounkel_untangling_2019} to be in the group.
Galactic positions are determined and plotted only for stars with parallax
signal-to-noise exceeding 20.
The location of the Sun is shown on the plots.
The non-uniform ``clumps'' might be
an artifact of the data processing steps performed by \citet{kounkel_untangling_2019}.
We therefore only consider stars in the immediate kinematic group
around \sn. 
The tangential velocities relative to \sn\ are shown in the bottom right panel.
These are computed by assuming that every star has the same three-dimensional
spatial velocity as \sn, where we assume a systemic radial velocity of
$-16.7 \pm 0.2$\,\kms\ based on the reconnaissance spectra obtained by
A.~Howard on HIRES and D.~Latham on TRES.
The relevant projection effects are then taken into account,
as discussed by {\it e.g.}, \citet{Meingast2021} and {\bf L.~Bouma et al (2021, submitted)}.
